Assignment 3

### 2015-02-16 rmtw/a3/latex8.tex
Spellcheck

@@

\SubSection{Research Question(s)}
RQ: How is change managed in multi-paradigm environments?
SRQ1: What are the challanges of implementing change in multi-paradigm environments?
SRQ2: How can a company determine if a change will conflict with the currently used development paradigms?
SRQ3: How can an organisation's development paradigm be used as a basis for deciding which changes to adopt?

@@

\begin{itemize}
\item Create questions for your interviews (include the questions in your report)
\item Discuss validity threats
\item Triangulation = counteract research bias
\item In meth, mention how the interviewees were selected and contacted (you have a gatekeeper which selects the people for you)
\item Mention how many of each role and why each role was included (triangulation)
\item convenience sampling (yo uhave contact at company already and use them) and maximum varation (i aim to have as many as possible)
\item Mention how the company was selected and what the criteria was (there was some lazy w)
\item the documents analysis (triangulation) will mostly be used to verify what the change agents say
\end{itemize}

\Section{Threats to Validity}

>>>>

give examples of what we mean by changes, i.e. implementing scrum, TDD.

@@

\SubSection{Research Question(s)}
RQ: How is change managed in multi-paradigm environments?
SRQ1: What are the challenges of implementing change in multi-paradigm environments?
SRQ2: How can a company determine if a change will conflict with the currently used development paradigms?
SRQ3: How can an organisation's development paradigm be used as a basis for deciding which changes to adopt?

@@

\begin{itemize}
\item Create questions for your interviews (include the questions in your report)
\item Discuss validity threats
\item Triangulation = counteract research bias
\item In meth, mention how the interviewees were selected and contacted (you have a gatekeeper which selects the people for you)
\item Mention how many of each role and why each role was included (triangulation)
\item convenience sampling (yo uhave contact at company already and use them) and maximum variation (i aim to have as many as possible)
\item Mention how the company was selected and what the criteria was (there was some lazy w)
\item the documents analysis (triangulation) will mostly be used to verify what the change agents say
\end{itemize}

\Section{Threats to Validity}
%getting too close, potential bias
%change manager bias, if they implemented
%generalisability

%Check text for more.
%% Talk about generalisability tomorrow with willski

%gatekeeper to help sample, he could, in some way, select persons that are positive. We give up control to the judgement of the gatekeeper

%only doing it at EPG.
%doing it at different times, only one company -> generalise
